Appendix 1: Preregistered analysis with simulated data

### 2025-04-23 preregistration.Rmd
missing data

Number of life time donations (bd02) and number of donations in last years (bd03) and likert scale measured variables (po01-3, si01-03, it01-03, ac01-04, iv01-03) will be treated as numeric. Last donation date (bd04) will transformed "bd04 / 10^-(1 - str_length(as.numeric(max(bd04))))".

@@

c. Latent factor model with robust estimator

d. Latent factor model with boostrapping

@@

The survey platform only reports completed questionnaires and all questions are obligatory. Hence there will be no missing data.

@@

Qualitative content analysis will be conducted on participants answers to the open-response question (What do you remember about the first time you donated blood?). Bivariate correlations will be calculated to compare donors’ willingness to respond to a call-out to past blood donation behaviour, psychological ownership, self-identity, and intention to donate blood.

>>>>

Number of life time donations (bd02) and number of donations in last years (bd03) and likert scale measured variables (po01-3, si01-03, it01-03, ac01-04, iv01-03) will be treated as numeric. Last donation date (bd04) will transformed to days from last donation by subtracting date of questionnaire response from date of last donation.

@@

c. Sum score model with FIML for missing data

d. Latent factor model with robust estimator

e. Latent factor model with boostrapping

f. Latent factor model with FIML for missing data

@@

Missing data will be analysed (see Appendix 1 for details) for possible biases and Little’s MCAR test carried out to assess randomness of missing data. Models using robust maximum likelihood or bootstrapped maximum likelihood estimation will be fitted with "listwise" deletion of missing data and in addition models using maximum likelihood estimator and "full information maximum likelihood" approach to deal with missing data will be fitted. All these results will be reported and discussed, acknowledging that there is no well-accepted method of dealing with data that is not missing at random

@@

Qualitative content analysis will be conducted on participants answers to the open-response question (What do you remember about the first time you donated blood?). Bivariate correlations will be calculated to compare donors’ willingness to respond to a call-out to past blood donation behaviour, psychological ownership, self-identity, and intention to donate blood.
If there is sufficient data we will stratify models by sex.
Model improvements will be considered if deemed appropriate.
